The Rockerverse: Packages and Applications for Containerisation with R

### 2020-03-02 manuscript.Rmd
add little snippet for getting a list of GitHub handles
add author contributions for Jason Williams, Tyson Swetnam - fix incorrect link in CyVerse section

      #- \orcid{}

@@

    # https://github.com/benmarwick/

@@

    # https://github.com/nolistic/

@@

      #- \orcid{NA}

@@

    # https://github.com/jnolis/

@@

[CyVerse](https://cyverse.org) is an open source, NSF-funded cyberinfrastructure platform for the life sciences providing easy access to computing and storage resources \citep{merchant_iplant_2016}.
CyVerse's a browser-based 'data science workbench' is called [Discovery Environment](https://cyverse-de.github.io/) (DE).
DE uses a combination of [HTCondor](https://research.cs.wisc.edu/htcondor/) and Kubernetes for orchestrating container-based analysis and integrates with external HPC, i.e., [NSF-XSEDE](https://www.xsede.org/), through [TAPIS](https://www.tacc.utexas.edu/tapis) API's.
In addition, CyVerse provides a multi-petabyte Data Store based on [iRODS](https://irods.org/) with shared access by users.
The DE runs Docker containers on demand, with users able to integrate bespoke containers from DockerHub or other registries \citep{devisetty_bringing_2016}.
Rocker integration in the DE is designed to provide life science researchers with scalable, compute-intensive R analysis capabilities needed for large and complex datasets (e.g., genomics/multi-omics, GWAS, phenotypic data, spatial data etc.).
These capabilities give users flexibility similar to Binder, but allows containers to run on larger computational resources (RAM, CPU, Disk), and for longer periods of time (days to weeks).
The Rocker Project's RStudio and Shiny containers are integrated into the DE by deriving new images from Rocker images\footnote{See \href{https://github.com/cyverse-vice/}{https://github.com/cyverse-vice/} for \texttt{Dockerfile}s and configuration scripts; images are auto-built on DockerHub at \href{https://hub.docker.com/u/cyversevice}{https://hub.docker.com/u/cyversevice}.}.
These images include a reverse proxy using `nginx` to handle communication with CyVerse's authentication systems, which allow users to invite other registered users to securely access the same instance \citep{rstudio_proxy_2020}.
The images further include specific tools, such as the CLI utility `icommands` to access iRODS.
Users can reference the same base image and add packages to further customize their R environment, or they can use CyVerse's image registry where a user's published, i.e., publicly available, containers are held for additional reproducibility.
CyVerse user accounts are free (with some limitations for non-US users) and the [CyVerse Learning Center](https://learning.cyverse.org/) allows community members to document their containers to support training and education.

@@

The ordering of authors following DN and DE is alphabetical.
DN conceived the article idea, \href{https://github.com/nuest/rockerverse-paper/issues/3}{initialised the formation of the writing team}, wrote sections not mentioned below, and revised all sections.
DB wrote the section on \pkg{outsider}.
GD contributed the CARD.com use case.
DE wrote the introduction and the section about containerisation and Rocker Project, and reviewed all sections.
RC \& EH contributed to the section on interfaces for Docker in R (_dynverse_ and `dynwrap`).
DC contributed content on Gigantum.
ME contributed to the section on processing and deployment to cloud services.
CF wrote paragraphs about \pkg{r-online}, \pkg{dockerfiler}, \pkg{r-ci} and \pkg{r-db}.
SL contributed content on RStudio's usage of Docker.
BM wrote the section on research compendia and made the project Binder ready.
HN \& JN co-wrote the section on the T-Mobile use case.
KR wrote the section about \pkg{holepunch}.
NR wrote paragraphs about shared work environments and GPUs.
LS \& NT wrote the section on Bioconductor.
CW wrote the sections on Whole Tale and contributed the publication reproducibility audit use case.
NX contributed content on \pkg{liftr}.
LK contributed content on \pkg{dockr}.
PS wrote the paragraphs about GitLab CI/CD pipelines with Shinyproxy and OpenFaaS R templates.
All authors approved the final version.
This articles was collaboratively written at \href{https://github.com/nuest/rockerverse-paper/}{https://github.com/nuest/rockerverse-paper/}.
The \href{https://github.com/nuest/rockerverse-paper/graphs/contributors}{contributors page}, \href{https://github.com/nuest/rockerverse-paper/commits/master}{commit history}, and \href{https://github.com/nuest/rockerverse-paper/issues/}{discussion issues} provide a detailed view on the respective contributions.

@@

>>>>

@@

    # https://github.com/benmarwick

@@

    # https://github.com/nolistic

@@

@@

    # https://github.com/jnolis

@@

[CyVerse](https://cyverse.org) is an open source, NSF-funded cyberinfrastructure platform for the life sciences providing easy access to computing and storage resources \citep{merchant_iplant_2016}.
CyVerse's a browser-based 'data science workbench' is called [Discovery Environment](https://cyverse.org/discovery-environment) (DE).
DE uses a combination of [HTCondor](https://research.cs.wisc.edu/htcondor/) and Kubernetes for orchestrating container-based analysis and integrates with external HPC, i.e., [NSF-XSEDE](https://www.xsede.org/), through [TAPIS](https://www.tacc.utexas.edu/tapis) API's.
In addition, CyVerse provides a multi-petabyte Data Store based on [iRODS](https://irods.org/) with shared access by users.
The DE runs Docker containers on demand, with users able to integrate bespoke containers from DockerHub or other registries \citep{devisetty_bringing_2016}.
Rocker integration in the DE is designed to provide life science researchers with scalable, compute-intensive R analysis capabilities needed for large and complex datasets (e.g., genomics/multi-omics, GWAS, phenotypic data, spatial data etc.).
These capabilities give users flexibility similar to Binder, but allows containers to run on larger computational resources (RAM, CPU, Disk), and for longer periods of time (days to weeks).
The Rocker Project's RStudio and Shiny containers are integrated into the DE by deriving new images from Rocker images\footnote{See \href{https://github.com/cyverse-vice/}{https://github.com/cyverse-vice/} for \texttt{Dockerfile}s and configuration scripts; images are auto-built on DockerHub at \href{https://hub.docker.com/u/cyversevice}{https://hub.docker.com/u/cyversevice}.}.
These images include a reverse proxy using `nginx` to handle communication with CyVerse's authentication systems, which allow users to invite other registered users to securely access the same instance \citep{rstudio_proxy_2020}.
The images further include specific tools, such as the CLI utility `icommands` to access iRODS.
Users can reference the same base image and add packages to further customize their R environment, or they can use CyVerse's image registry where a user's published, i.e., publicly available, containers are held for additional reproducibility.
CyVerse user accounts are free (with some limitations for non-US users) and the [CyVerse Learning Center](https://learning.cyverse.org/) allows community members to document their containers to support training and education.

@@

The ordering of authors following DN and DE is alphabetical.
DN conceived the article idea, \href{https://github.com/nuest/rockerverse-paper/issues/3}{initialised the formation of the writing team}, wrote sections not mentioned below, and revised all sections.
DB wrote the section on \pkg{outsider}.
GD contributed the CARD.com use case.
DE wrote the introduction and the section about containerisation and Rocker Project, and reviewed all sections.
RC \& EH contributed to the section on interfaces for Docker in R (_dynverse_ and `dynwrap`).
DC contributed content on Gigantum.
ME contributed to the section on processing and deployment to cloud services.
CF wrote paragraphs about \pkg{r-online}, \pkg{dockerfiler}, \pkg{r-ci} and \pkg{r-db}.
SL contributed content on RStudio's usage of Docker.
BM wrote the section on research compendia and made the project Binder ready.
HN \& JN co-wrote the section on the T-Mobile use case.
KR wrote the section about \pkg{holepunch}.
NR wrote paragraphs about shared work environments and GPUs.
LS \& NT wrote the section on Bioconductor.
CW wrote the sections on Whole Tale and contributed the publication reproducibility audit use case.
NX contributed content on \pkg{liftr}.
LK contributed content on \pkg{dockr}.
PS wrote the paragraphs about GitLab CI/CD pipelines with Shinyproxy and OpenFaaS R templates.
CV wrote the section on the usage of Docker containers in Dodona.
TS and JW wrote the section on CyVerse. 
All authors approved the final version.
This articles was collaboratively written at \href{https://github.com/nuest/rockerverse-paper/}{https://github.com/nuest/rockerverse-paper/}.
The \href{https://github.com/nuest/rockerverse-paper/graphs/contributors}{contributors page}, \href{https://github.com/nuest/rockerverse-paper/commits/master}{commit history}, and \href{https://github.com/nuest/rockerverse-paper/issues/}{discussion issues} provide a detailed view on the respective contributions.

@@

```{bash collab_handles, eval=FALSE, include=FALSE}
cat manuscript.Rmd | grep '    # https://github.com/' | sed 's|    # https://github.com/|@|'
```
